Carbon Management Strategies for a Climate-Neutral European Economy

### 2023-12-30 report/submissions/journal/cover_letter/letter.tex
review cover letter

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System”. This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes to the critical discourse on climate-neutral energy systems in Europe.

@@

		Our analysis not only confirms the role of hydrogen and carbon dioxide transport systems in providing crucial flexibilities to carbon-neutral energy systems. It also illustrates how their combination enhances energy efficiency and social welfare. We demonstrate that a hydrogen grid is optimally used to transport low-cost hydrogen from regions with abundant renewable resources to distributed carbon sources, such as industrial clusters and biomass combustion plants, to enable on-site synthetic fuel production. Conversely, a carbon dioxide network efficiently transports low-cost carbon from point sources near the coast to sequestration sites for permanent storage. Such an approach increase carbon capture rates from biomass combustion and reduces reliance on cost-intensive direct air capture. Furthermore, the benefits of deploying both networks are amplified under a net carbon-removal target.
		As underscored by our analysis, the integration of hydrogen and carbon dioxide networks into European energy policy is vital for a resilient, carbon-neutral, or negative future energy system.

>>>>

		%%%%%%%%%%% 	Text   %%%%%%%%%%%%%%
		Thank you for the opportunity to submit our manuscript to Nature Energy. We are pleased to present our paper titled “\hydrogen{} and \carbon{} Network Strategies for the European Energy System.” This collaborative effort from researchers at the Institute of Energy Technology, Technical University of Berlin, contributes significantly to the critical discourse on climate-neutral energy systems in Europe.

@@

		Our analysis not only confirms the role of hydrogen and carbon dioxide transport systems in providing crucial flexibilities to carbon-neutral energy systems, but it also illustrates how their combination enhances energy efficiency and social welfare. We demonstrate that a hydrogen grid is optimally used to transport low-cost hydrogen from regions with abundant renewable resources to distributed carbon sources, such as industrial clusters and biomass combustion plants, to enable on-site synthetic fuel production. Conversely, a carbon dioxide network efficiently transports low-cost carbon from point sources near the coast to sequestration sites for permanent storage. Such an approach increases carbon capture rates from biomass combustion and reduces reliance on cost-intensive direct air capture. Furthermore, the benefits of deploying both networks are amplified under a net carbon-removal target.

		As underscored by our analysis, the integration of hydrogen and carbon dioxide networks into European energy policy is vital for a resilient, carbon-neutral, or negative future energy system.
